Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-12-11 paper/ms.tex
updated discussion

\begin{figure}
\begin{center}
\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_degree2.pdf}  
\end{center}
\caption{Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Ouchi2010} . The error
bars in the theoretical data correspond to the quadratic average of
the fitting errors for each mock
survey \label{fig:correlation_parameters}} 
\end{figure}

@@

We end up with $XX$ models, out of $9000$ initial guesses, consistent
with observations. In order to discuss these results we now
define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$, to use it together with the occupation
fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ to
classify all the successful models into two families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: XX models. 
\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: XX models 
\end{itemize}
%
A complete parameter list is presented in Table
\ref{table:firstfamily} and Table \ref{table:secondfamily}. There are
two interesting feature in these families. First, the occupation
fraction can take any value from $0.1$ to $1.0$. Second, the halos
hosting LAEs all have a narrow mass range $\Delta M\leq 1.0$.

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.4 &10.7 & 0.1& 0.3 \\
 10.5 &10.9 & 0.1& 0.4 \\
 10.5 &11.0 & 0.1& 0.5 \\
 10.6 &10.8 & 0.2& 0.2 \\
 10.6 &11.2 & 0.1& 0.6 \\
 10.6 &11.3 & 0.1& 0.7 \\
 10.6 &11.4 & 0.1& 0.8 \\
 10.6 &11.5 & 0.1& 0.9 \\
 10.6 &11.6 & 0.1& 1 \\
 10.6 &11.7 & 0.1& 1.1 \\
 10.7 &11.0 & 0.2& 0.3 \\
 10.8 &11.2 & 0.2& 0.4 \\
 10.8 &11.3 & 0.2& 0.5 \\
 10.8 &11.4 & 0.2& 0.6 \\
 10.9 &11.7 & 0.2& 0.8 \\
 10.9 &11.8 & 0.2& 0.9 \\
 10.9 &11.9 & 0.2& 1 \\
 10.9 &12.0 & 0.2& 1.1 \\
 10.9 &12.1 & 0.2& 1.2 \\
 10.9 &12.2 & 0.2& 1.3 \\
 10.9 &12.3 & 0.2& 1.4 \\
 10.9 &12.6 & 0.2& 1.7 \\
 10.9 &12.8 & 0.2& 1.9 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

@@

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_degree2.pdf}  
\end{center}
\caption{Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green line to observations by \citet{Ouchi2010}. The error
bars in the theoretical data correspond to the quadratic average of
the fitting errors for each mock
survey \label{fig:correlation_parameters}} 
\end{figure}

@@

We end up with $40$ consistent models, out of the initial set of
$9000$. To facilitate the discussion of these results we define a new
quantity, the halo mass range $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$. This quantity together with the occupation
fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ allows us
to clasify all the successful models into three families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.2$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: 16 models. 
\item[(2)] High $f_{\rm occ}> 0.2$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: 17 models

\item[(3)] Models with low occupation $f_{\rm occ}\leq 0.2$ fraction
  and high $\Delta M>1.0$: 7 models
\end{itemize}

{\bf The models in the third family are barely consistent with the
  constraints from the ACF. They have mean values of $\theta_0$
  outside the observational uncertainties in that parameter, but have
  been included as consistent because their error bars overlap. These
models they have another particular feature: their minimum mass is
$M_{\rm min}=10^{10.9}\hMsun$. In what follows we exclude these models
from the discussion.}

A complete parameter list for the three families is presented in Table
\ref{table:firstfamily}, Table \ref{table:secondfamily} and Table
\ref{table:thirdfamily}. There are two interesting feature in these
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$.

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.4 &10.7 & 0.1& 0.3 \\
 10.5 &10.9 & 0.1& 0.4 \\
 10.5 &11.0 & 0.1& 0.5 \\
 10.6 &10.8 & 0.2& 0.2 \\
 10.6 &11.2 & 0.1& 0.6 \\
 10.6 &11.3 & 0.1& 0.7 \\
 10.6 &11.4 & 0.1& 0.8 \\
 10.6 &11.5 & 0.1& 0.9 \\
 10.6 &11.6 & 0.1& 1 \\
 10.7 &11.0 & 0.2& 0.3 \\
 10.8 &11.2 & 0.2& 0.4 \\
 10.8 &11.3 & 0.2& 0.5 \\
 10.8 &11.4 & 0.2& 0.6 \\
 10.9 &11.9 & 0.2& 1.0 \\
 10.9 &11.7 & 0.2& 0.8 \\
 10.9 &11.8 & 0.2& 0.9 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}
List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.6 &11.7 & 0.1& 1.1 \\
 10.9 &12.0 & 0.2& 1.1 \\
 10.9 &12.1 & 0.2& 1.2 \\
 10.9 &12.2 & 0.2& 1.3 \\
 10.9 &12.3 & 0.2& 1.4 \\
 10.9 &12.6 & 0.2& 1.7 \\
 10.9 &12.8 & 0.2& 1.9 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:thirdfamily}List of parameters for the third
  family of models. Wide mass range $\Delta M> 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.2$.} 
\end{table}
